\propertitle

### 2020-03-17 replies1_ncomp.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-17T00:35:35+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

In any case, please note that we avoid speaking about
\enquote{significance}, also as recommended by the American Statistical
Association in their recent official statements \citep{asa2016}[see
especially \sect~2]{asa2019}. When comparing hypotheses $M_{i}$ we want
their full post-data probabilities $\p(M_{i} \| D)$, with their continuum
of cases. Other researchers are of course free to make dichotomies if they
like; but we personally agree with the American Statistical Association
that any threshold is unnecessary and arbitrary. If a \emph{choice} among
the hypotheses has to be made for some purpose (say, hardware algorithm
implementation in some automated device), such choice requires not only the
probabilities $\p(M_{i}\|D)$, but also the utility/loss matrix for the
various choices conditional on the various hypotheses
\citep{kadaneetal1980b}. The choice is then made by maximization of the
expected utility, a procedure dictated by some simple rational desiderata
\citep{fishburn1981,bernardoetal1994_r2000}[\chap~13]{jaynes1994_r2003}.
Some utility matrices can even lead to choosing the hypothesis having
\emph{lower} post-data probability; this frequently happens in medical
decision problems, see \eg\ \textcite{soxetal1988_r2013}.

@@

@@

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-17T01:02:47+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

In any case, please note that we avoid speaking about
\enquote{significance}, also as recommended by the American Statistical
Association in their recent official statements \citep{asa2016}[see
especially \sect~2]{asa2019}. When comparing hypotheses $M_{i}$ we want
their full post-data probabilities $\p(M_{i} \| D)$, with their continuum
of cases. We respect the freedom of other researchers to make dichotomies,
if they so prefer. But our personal point of view agrees with the American
Statistical Association: any threshold is unnecessary and arbitrary. If a
\emph{choice} among the hypotheses has to be made for some purpose (say,
hardware algorithm implementation in some automated device), such choice
requires not only the probabilities $\p(M_{i}\|D)$, but also the
utility/loss matrix for the various choices conditional on the various
hypotheses \citep{kadaneetal1980b}. The choice is then made by maximization
of the expected utility, a procedure dictated by some simple rational
desiderata
\citep{fishburn1981,bernardoetal1994_r2000}[\chap~13]{jaynes1994_r2003}.
Some utility matrices can even lead to choosing the hypothesis having
\emph{lower} post-data probability; this frequently happens in medical
decision problems, see \eg\ \textcite{soxetal1988_r2013}.

@@

*** equiv to unsystematic sampling for extended recording arrays

@@

*** analogous to \enquote{design} in survey sampling
